---
title: "Calculate equilibrium isotope effect"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output:
  html_document: 
    df_print: paged
    toc: yes
    toc_float: true
    code_folding: show
editor_options:
  chunk_output_type: inline
---

```{r "setup", warning=FALSE, message=FALSE}
library(tidyverse)
library(latex2exp)
```

# Define physical constants

```{r}
h <- 6.6261 * 10^(-27)  # cm2 g s-1 planck constant
k <- 1.3807 * 10^(-16)  # cm2 g s-2 K-1 boltzman constant

# NOTE: not using c as the speed of light variable here (sol instead) 
# because of the special meaning of c() in R
sol <- 2.99 * 10^10       # cm s-1 speed of light
```

# Helper functions to calculate partition function ratios

```{r}
source(file.path("libs", "calc_m_ratio.R"))
source(file.path("libs", "calc_vib_freq_ratio.R"))
source(file.path("libs", "calc_U.R"))
source(file.path("libs", "calc_low_T_term_ratio.R"))
source(file.path("libs", "calc_high_T_term_ratio.R"))
```

# CO2 <-> Water equilibrium

We are looking at the reaction:

$$
\frac{1}{2}\cdot C^{16}O_2 + 1\cdot H_2^{18}O \leftrightarrow \frac{1}{2}\cdot C^{18}O_2 + 1\cdot H_2^{16}O
$$

For this reaction, the fractionation factor is:

$$
\alpha_{CO_2/H_2O} = K_{eq} = \frac{\left(Q^* / Q\right)^{1/2}_{CO_2}}{\left(Q^* / Q\right)_{H_2O}}
$$

Overall partition function ratios for each compound:

$$
\begin{align}
\frac{Q^*}{Q} &= \left( \frac{m^*}{m} \right)^{3n/2} 
\frac{\sigma}{\sigma^*} 
\prod_i \frac{\nu^*_i}{\nu_i} 
  \frac{e^{-U^*_i /2}}{e^{-U_i /2}} 
  \frac{1 - e^{-U_i}}{1 - e^{-U_i^*}} \\
\text{with:} \, 
  U &= \frac{h \nu}{kT} = \frac{h c \omega}{kT}
\end{align}
$$



# Wave numbers and isotopes

Import the wave numbers from the wave_numbers.xlsx file. Import the isotopes from the system.xlsx file.

```{r}
# wave numbers

```

```{r}
# isotopes

```

```{r}
# combination (store in compounds variable)

```


# Temperatures to probe

Define which temperatures we want to look at 

```{r}
# define temperature range

```

# System

```{r}
# put together whole system

```

## Calculations

# Components of the partition function ratio

```{r}
# calculate all the different components of the partition function ratios (QR)
# QR_m, QR_symmetry, QR_vib, QR_low_T, QR_high_T

```

# Plot the components

```{r, fig.width=10, fig.height=8}

```


# Total partition function ratio

Remember:

$$
\frac{Q^*}{Q} = \left( \frac{m^*}{m} \right)^{3n/2} 
\frac{\sigma}{\sigma^*} 
\prod_i \frac{\nu^*_i}{\nu_i} 
  \frac{e^{-U^*_i /2}}{e^{-U_i /2}} 
  \frac{1 - e^{-U_i}}{1 - e^{-U_i^*}}
$$


```{r}
# calculate the total from the parts

```


# Actual fractionation factors


```{r}
# calculate the fractionation factors
```

# Plotting the fractionation factor

```{r}

```

